LHC abort gap monitor electronics upgrade

### 2024-04-04 paper.tex
added installation picture to the tex document
added names of sections and subsection with dummy text

\section{system architecture}
basic methodology how to monitor this area is to exploit the synchrotron
radiation light (SL). This phenomena appears when a particle is moving on a
circular trajectory. The energy of the beam is proportional to the changes in
the radiated spectrum. With increasing energy, the light is shifted towards
shorter wavelengths. Since the LHC works with the energy from 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
    \caption{BSRA Chain}
    \label{fig:bsra_chain}
\end{figure}

\subsection{Technical Solution}
        %Utilization of Analogue Integrator ASIC
        %40 MHz Analogue-to-Digital Converter (ADC)
        %Operation Since 2010
        %Reasons for Obsolescence
        %Digital Signal Processing Approach why and outcomes

        \begin{figure}[!tbh]
            \centering
            \includegraphics[width=\columnwidth]{bsra_daq.pdf}
            \caption{upgraded amplifier}
            \label{fig:amplifier}
        \end{figure}

\section{New fully digitized AGM}

        \begin{figure}[!tbh]
            \centering
            \includegraphics[width=\columnwidth]{amp_schematics.pdf}
            \caption{upgraded amplifier}
            \label{fig:amplifier}
        \end{figure}

% \section{Comparison of Implementations}
%     \input{tables/system_comparison.tex} 
%     %compare the changes and comment the expected changes

\section{Recent Measurements}

    \begin{figure}[!htb]
      \begin{center}
          \scalebox{0.54}{\input{plots/ions.pgf}}
          \caption{Comparison of AGMs}
          \label{fig:comparison_chart}
      \end{center}
    \end{figure}

% \section{Discussion}
%     \subsection{Significance of the Upgrade}
%     \subsection{Future Implications}
%     % \subsubsection{Potential for Further Enhancements or Modifications}
%     % \subsubsection{Integration with Other Accelerator Technologies}

\section{Conclusion}

\input{acknowledgements}
\input{appendix}
\input{bibliography}

>>>>

\section{System architecture}
basic methodology how to monitor this area is to exploit the synchrotron
radiation light (SL). This phenomena appears when a particle is moving on a
circular trajectory. The energy of the beam is proportional to the changes in
the radiated spectrum. With increasing energy, the light is shifted towards
shorter wavelengths. Since the LHC works with the energy from

\subsection{Working principle}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
    \caption{BSRA Chain}
    \label{fig:bsra_chain}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Current Solution}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Constraints and Limitations}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{System Upgrade}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
%Utilization of Analogue Integrator ASIC
%40 MHz Analogue-to-Digital Converter (ADC)
%Operation Since 2010
%Reasons for Obsolescence
%Digital Signal Processing Approach why and outcomes

\subsection{Acquisition System}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\section{}
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_daq.pdf}
    \caption{upgraded amplifier}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Low band Amplifier}
% \input{tables/system_comparison.tex} 
%compare the changes and comment the expected changes
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
    \caption{upgraded amplifier}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Installation in LHC}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{installation.jpg}
    \caption{installation picture}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Control Interface}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{installation picture}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Measurements}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!htb]
    \begin{center}
        \scalebox{0.54}{\input{plots/ions.pgf}}
        \caption{Comparison of AGMs}
        \label{fig:comparison_chart}
    \end{center}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Discussion}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Conclusion}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

% \input{acknowledgements}
% \input{appendix}
\input{bibliography}
